The Astropy Project

### 2017-12-09 main.tex
Modified the order of the comparison of the different packages
The table now is ordered so the packages that have a closer agreement
are shown together. This way I find it easier to find how they cluster
between themselves.
comments by bspiorz

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank numfocus and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that developers on
their staff can contribute their time to the development of
\astropy projects.

>>>>

\acknowledgments The \astropy community is supported by and makes use
of a number of organizations and services outside the traditional
academic community. We thank Google for financing and organizing the
Google Summer of Code (GSoC) program, that has funded severals
students per year to work on \astropy related projects over the
summer. These students often turn into long-term contributors. We also
thank NumFOCOS and the Python Software Foundation for financial
support. Within the academic community, we thank
institutions that make it possible that astronomers and other developers on
their staff can contribute their time to the development of
\astropy projects.
